---
title: "The InterEco Tool"
---

**1) Getting started**

To get started with making your InterEco website, you will first need to install some R packages.

```{}
```

*Setup R on your computer*

If you do not have R on your machine, first install [R](https://cran.r-project.org/). It's also a good idea to download RStudio, a popular integrated development environment for coding with R, created by posit (\[download\](https://posit.co/products/open-source/rstudio/)).

*Download necesary R packages*

```{r}
# here download all relevant packages for this project
# needs to check if they are installed and if not install, then load all the libraries.

```

**Working with our example dataset**

We will work with dataset from study in XX et al. describe din our paper

```{r}
data(antdata)
```

**Setting up your InterEco webpage**

first of all, set up an empty sshiny app. we will build this nefpre we add contenty...

```{r}
# add empty code chunk - shiny framework
```

**2) Setting up you landing page tab**

here we are setting up our landing page are editing the code between xxx and xxx.

The landing page is intended to XXXX.

In our ant example, we...

```{r}

```
